Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-05-12 Paper.Rmd
jrny conts rly

@@

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods \@10.2307/1830691. Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

@@

Nelson (1970) @10.2307/1830691 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. A product's Total Cost consists of both Search Cost and Product Cost. This Search Cost is higher for Experience Goods, in other words, information search is costlier for Experience Goods than Search Goods.

To explain it in a more generalized way, let's also define what "search" is. Nelson (1970) @10.2307/1830691 defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search". People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search. This is why search is costlier for Experience Goods. For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it. Even though a car has experience attributes, with this logic it is considered as a search good @klein1998.

@@

Humans tend to care about losses more than same amount of gains. Losing 100\$ is psycholgically much more impactful than finding 100\$. This behavior is best explained by "loss aversion" from Behavioral Economics. [@kahneman1979; @schindler2017]. Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses @herr1991.

Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than positive ones. --, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones. --, higher negative dominance --
A combination of equally negative and positive cues results in more negative impressions. --, and various negative differentiations -- Negative cues produce more diverse individual responses than positive ones. --[ @rozin2001; @sen2007; @eslami2018].

@@

# Methodology

@@

@@

>>>>

```{r, echo=FALSE}
library(tidyverse)
library(tidytext)
library(scales)
library(AER)
library(ggfortify)
library(lubridate)

options(scipen = 20)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 8,
                      echo = FALSE)
```

@@

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @10.2307/1830691 . Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

@@

Nelson (1970) [@10.2307/1830691] differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. A product's Total Cost consists of both Search Cost and Product Cost. This Search Cost is higher for Experience Goods, in other words, information search is costlier for Experience Goods than Search Goods.

To explain it in a more generalized way, let's also define what "search" is. Nelson (1970) [@10.2307/1830691] defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search". People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search. This is why search is costlier for Experience Goods. For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it. Even though a car has experience attributes, with this logic it is considered as a search good @klein1998.

@@

Humans tend to care about losses more than same amount of gains. Losing 100\$ is psychologically much more impactful than finding 100\$. This behavior is best explained by "loss aversion" from Behavioral Economics. [@kahneman1979; @schindler2017]. Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses @herr1991.

Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than positive ones. --, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones. --, higher negative dominance -- A combination of equally negative and positive cues results in more negative impressions. --, and various negative differentiations -- Negative cues produce more diverse individual responses than positive ones. --[@rozin2001; @sen2007; @eslami2018].

@@

# Research Methodology

@@

The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 @10.5555/1593511. The scraper got the customer reviews from IMDB and BestBuy. The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America. Both websites host a great amount of online reviews. After the data was collected it was further transformed and analyzed with the help of R Programming Language [@RCore; @Tidyverse; @Tidytext].

Online Customer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited. It is nearly impossible to evaluate a movie before watching it. Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective perspectives (writing, production quality etc.). There are also numerous studies that analyzed movies as experience goods[@10.2307/1830691; @liu2014; @ghose2006; @baek2012; @lee2016].

BestBuy is a very big electronics retailer and because of this the website offers a sizable number of OCR for search goods. Contrary to experience goods, search goods usually have more objectively quantifiable traits. For example, resolution or screen size of a TV, RAM or GPU of a Laptop, storage or battery lifetime of a Smart Phone. Additionally, in the literature, TVs, Laptops and Phones were used as search goods [@mudambi2010; @sun2019; @baek2012; @ren2019]. Therefore, we collected search goods data from BestBuy.

-   mention that channels can change the way we perceive search and experience goods.

From IMDB reviews of 22 movies were collected as experience goods. In total 22 movies account for 31,863 reviews. From BestBuy, total of 383,357 reviews were collected as search goods. Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones. However, in the data there are many reviews that were never voted. To make sure that we are analyzing reviews that were actually read by people, we set a threshold for Total Reviews as five. In other words, we removed reviews that have less than 5 Total Votes [@choi2020; @baek2012]. At the very end, we were left with 15,024 observations for experience goods and 8,042 observations for search goods. It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times.

It should be noted that in IMDB data there were cases (20 observations to be exact) where the same reviews were written by different user names. We removed all duplicates along with original reviews because the reviews had different helpfulness ratios.

@@

```{r Data_Prep_Experience}
# Experience Goods

## Read the Data

files <- dir()

files <- files[str_detect(files, "movie_.+")]

movies_data <- map_dfr(files, read_csv, show_col_types = FALSE)

## Removing reviews without Ratings
movies_data <- movies_data %>% 
  filter(!is.na(Rating))

## Creating Helpul and Total Votes Variables 
movies_data <- movies_data %>% 
  separate(Rating, into = c("Rating", "Total"), sep = "/", ) %>% 
  select(-Total) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Rating = as.double(Rating)) %>% 
  mutate(Helpfulness = Helpful_Vote / Total_Vote) %>% 
  mutate(Rating = Rating/2)

## Removing All the Duplicated Reviews including the original since same reviews were written by differend user names
movies_data <- movies_data %>% 
  mutate(Rev_dup = duplicated(Review) | duplicated(Review, fromLast = TRUE)) %>% 
  filter(Rev_dup == 0)

## Words
movies_data <- movies_data %>% 
  mutate(Doc_ID = row_number())

## Word Count
movies_agg <- movies_data %>% 
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  count(Doc_ID, name = "Word_Count")

movies_data <- movies_data %>% 
  inner_join(movies_agg, by = "Doc_ID")

## Emotion Sentiments (EmoLex)
### log10(Proportion of Emotion Words * 100)

sentiments_agg <- movies_data %>%
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  inner_join(get_sentiments("nrc")) %>% 
  count(Doc_ID, sentiment, name = "Sent_Count") %>% 
  pivot_wider(names_from = sentiment, values_from = Sent_Count, values_fill = 0)

movies_data <- movies_data %>% 
  full_join(sentiments_agg, by = "Doc_ID")

variables <- names(sentiments_agg)[-1]

movies_data <- movies_data %>% 
  mutate(across(.cols = all_of(variables), .fns = ~ifelse(is.na(.), 0, .) ))

movies_data <- movies_data %>% 
  mutate(across(.cols = all_of(variables), .fns = function(.) ./Word_Count*100))

movies_data <- movies_data %>% 
  mutate(across(.cols = variables, .fns = function(.) log10(. + 1)))

## Freshness (Timeline)
movies_data <- movies_data %>% 
  mutate(Date = dmy(Date, locale = "english"))

first_dates <- movies_data %>% 
  group_by(Movie) %>% 
  slice_min(order_by = Date, n = 1, with_ties = F) %>% 
  select(Movie, Date) %>% 
  rename(First_Date = Date)

movies_data <- full_join(movies_data, first_dates, by = "Movie") %>% 
  mutate(Freshness = as.integer(Date - First_Date))

```

```{r Data_Prep_Search}

# Search Goods
## Phone Data
phones_data <- read_csv("all_phone_reviews_15_03_22.csv", show_col_types = FALSE)

phones_data <- phones_data %>% 
  mutate(Product_Type = "Phone")

## Laptop Data
files <- dir()
files <- files[str_detect(dir(), "all_laptop_reviews.+")]
laptop_data <- map_dfr(files, read_csv, show_col_types = FALSE)
### Removing replicates that I couldn't detect earlier
laptop_data <- laptop_data %>% 
  filter(!Product_Name %in% c(
    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
  )) %>% 
  mutate(Product_Type = "Laptop")

## TV Data
tvs_data <- read_csv("all_tv_reviews_16_03_22.csv", show_col_types = FALSE)
tvs_data <- tvs_data %>% 
  mutate(Product_Type = "TV")

## Merging All 
search_goods <- phones_data %>% 
  bind_rows(tvs_data, laptop_data)

## Creating Total Votes variable Filtering Total Votes below 5

search_goods <- search_goods %>% 
  mutate(Total_Vote = Helpful + Unhelpful) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Helpfulness = Helpful / Total_Vote) %>% 
  mutate(is_Exp = 0)

search_goods <- search_goods %>% 
  mutate(Dupped = duplicated(Review)) %>% 
  filter(Dupped == 0)

## Word Counts

search_goods <- search_goods %>% 
  mutate(Doc_ID = row_number())

words_agg <- search_goods %>%
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  count(Doc_ID, name = "Word_Count")

search_goods <- search_goods %>% 
  inner_join(words_agg, by = "Doc_ID")

## Emotion Sentiments (EmoLex)
### log10(Proportion of Emotion Words * 100)

sentiments_agg <- search_goods %>%
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  inner_join(get_sentiments("nrc")) %>% 
  count(Doc_ID, sentiment, name = "Sent_Count") %>% 
  pivot_wider(names_from = sentiment, values_from = Sent_Count, values_fill = 0)

search_goods <- search_goods %>% 
  full_join(sentiments_agg, by = "Doc_ID")

variables <- names(sentiments_agg)[-1]

search_goods <- search_goods %>% 
  mutate(across(.cols = variables, .fns = ~ifelse(is.na(.), 0, .) ))

search_goods <- search_goods %>% 
  mutate(across(.cols = all_of(variables), .fns = function(.) ./Word_Count*100))

search_goods <- search_goods %>% 
  mutate(across(.cols = variables, .fns = function(.) log10(. + 1)))

## Freshness (Timeline)

search_goods <- search_goods %>% 
  mutate(Date = as_date(mdy_hm(Date, locale = "english")))

first_dates <- search_goods %>% 
  group_by(Product_Name) %>% 
  slice_min(order_by = Date, n = 1, with_ties = F) %>% 
  select(Product_Name, Date) %>% 
  rename(First_Date = Date)

search_goods <- search_goods %>% 
  full_join(first_dates, by = "Product_Name") %>% 
  mutate(Freshness = as.integer(Date - First_Date))
```

### Independent Variable
